Supplement to Example Manuscript Template for a Data Analysis Project

### 2025-04-23 products/manuscript/supplement/Supplementary-Material.qmd
Part 5 of MADA Project

>>>>

# List of irAEs:
Skin and subcutaneous tissue disorders:
Rash, pruritus, dermatitis, psoriasis
Gastrointestinal disorders:
Colitis, hepatitis, pancreatitis, enterocolitis, ileitis, ileocolitis
Nervous system disorders:
Myasthenia gravis, Graves disease, myelitis, encephalitis, neuritis, peripheral neuropathy
Endocrine disorders:
Hyperthyroidism, hypothyroidism, thyroiditis, thyrotoxicosis, adrenitis, adrenal insufficiency, hypogonadism, hyperparathyroidism, hypercortisolism, hypophysitis, hypoparathyroidism, hypocortisolism, autoimmune diabetes
Cardiac disorders: myocarditis, pericarditis, myocarditis
Respiratory, thoracic, and mediastinal_disorders:
Pneumonitis
Renal and urinary_disorders: 
Pyelonephritis, nephritis
